---
title: "Status of Nitrogen Dioxide in B.C. (2021-2023 & 2022-2024)"
output:
  pdf_document: envreportutils.internal::print_ver
topic: air
---

<!--
Copyright 2026 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed
under the License is distributed on an "AS IS" BASIS, WITHOUT WARRANTIES OR
CONDITIONS OF ANY KIND, either express or implied. See the License for the
specific language governing permissions and limitations under the License.
-->

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, 
                      warning = FALSE, error = FALSE, fig.width = 7)

library("readr")
library("dplyr")
library("tidyr")
library("here")
library("purrr")
library("ggplot2")
library("ggtext") # Ensure map legends formatted correctly
library("assertr")
library("rcaaqs")
library("envreportutils")
library("envreportutils.internal")
library("english")

knitr_latex_char <- function(x) {
  y <- gsub("\\\\", "\\\\textbackslash{}", x) # backslash has to be first!
  y <- gsub("([#$%&_])", "\\\\\\1", y) # Doesn't deal with { or } because of function{}
  y <- gsub("\\^", "\\\\textasciicircum{}", y)
  y <- gsub("~", "\\\\textasciitilde{}", y)
  return(y)
}

year_range <- "2022-2024"
year_range_previous <- "2021-2023"

# Data from 04_outputs.R
plots <- read_rds(here("data/datasets/rep_year_2024/print_plots.rds"))
plots_2023 <- read_rds(here("data/datasets/rep_year_2023/print_plots.rds"))
stn_plots <- read_rds(here("data/datasets/rep_year_2024/print_stn_plots.rds"))
print_summary <- read_rds(here("data/datasets/rep_year_2024/print_summary.rds"))
no2_results <- read_rds(here("data/datasets/rep_year_2024/no2_results.rds")) # From 03_analysis.R
no2_3yr_mgmt <- read_rds(here("data/datasets/rep_year_2024/no2_3yr_mgmt.rds"))
no2_1yr_mgmt <- read_rds(here("data/datasets/rep_year_2024/no2_1yr_mgmt.rds"))
stations_clean <- read_rds(here("data/datasets/rep_year_2024/stations_clean.rds"))

# Specify cutoffs from rcaaqs
no2_lvls <- achievement_levels %>%
  filter(parameter %in% c("no2_3yr", "no2_1yr"), lower_breaks != 0) %>%
  pull(lower_breaks, parameter)


p1 <- print_summary$percent_achieved[print_summary$metric == "no2_1yr"]
p3 <- print_summary$percent_achieved[print_summary$metric == "no2_3yr"]

n1a <- print_summary$n_achieved[print_summary$metric == "no2_1yr"]
n1  <- print_summary$n[print_summary$metric == "no2_1yr"]

n3a <- print_summary$n_achieved[print_summary$metric == "no2_3yr"]
n3  <- print_summary$n[print_summary$metric == "no2_3yr"]

same_pct <- isTRUE(all.equal(p1, p3))

no2_standards_sentence <- if (!same_pct) {
  paste0(
    "The annual standard was met at ", n1a, " of the ", n1, " stations (", p1,
    "%) for which valid data were obtained, while the 1-hour standard was met at ",
    n3a, " of the ", n3, " stations (", p3, "%) with sufficient data for analysis."
  )
} else {
  paste0(
    "The annual and 1-hour standards were met at ", p1,
    "% of stations with sufficient data (", n1a, "/", n1,
    " and ", n3a, "/", n3, " stations, respectively)."
  )
}

# 2023 results
year_prev <- 2023

no2_3yr <- get_caaqs(no2_3yr_mgmt) %>%
  filter(n_years > 1)

no2_1yr <- get_caaqs(no2_1yr_mgmt) %>%
  mutate(n_years = 1)


no2_results_combined <- bind_rows(no2_3yr, no2_1yr) %>%
  ungroup() %>%
  left_join(stations_clean, by = "site") %>%
  # Ensure only 1 analysis per site
  add_count(site, caaqs_year, metric) %>%
  assert(in_set(1), n) %>%
  # Clean up
  select(caaqs_year, airzone, 
         station_name = site, 
         region, 
         latitude = lat, 
         longitude = lon, 
         metric,
         n_years,	
         min_year,	
         max_year,
         metric_value_ambient,
         caaqs_ambient,
         excluded,
         metric_value_mgmt,
         mgmt_level,
         everything(), -n, -flag_daily_incomplete, -flag_yearly_incomplete) %>% 
  arrange(caaqs_year, airzone)


yrs_present <- sort(unique(no2_results_combined$caaqs_year))
summarise_year <- function(df, y) {
  az_achieved <- df %>%
                  filter(caaqs_year == y) %>%
                  nest(data = c(-metric, -caaqs_year)) %>%
                  mutate(data = map(data, ~airzone_metric(., keep = "station_name", station_id = "station_name"))) %>%
                  unnest(data) %>%
                  select(airzone, metric, caaqs_year, everything()) %>%
                  group_by(metric) %>%
                  summarise(az_achieved = sum(caaqs_ambient == "Achieved", na.rm = TRUE))
  df %>%
    filter(caaqs_year == y) %>%
    group_by(metric) %>%
    filter(!is.na(metric_value_ambient)) %>%
    summarise(
      year = y,
      n_stations = n(),
      n_achieved = sum(caaqs_ambient == "Achieved", na.rm = TRUE),
      pct_achieved = round(100 * n_achieved / n_stations),
      .groups = "drop")  %>%
      left_join(az_achieved, by = "metric")
}

summary_prev <- summarise_year(no2_results_combined, year_prev)

p1_prev <- summary_prev$pct_achieved[summary_prev$metric == "no2_1yr"]
p3_prev <- summary_prev$pct_achieved[summary_prev$metric == "no2_3yr"]

n1a_prev <- summary_prev$n_achieved[summary_prev$metric == "no2_1yr"]
n1_prev  <- summary_prev$n_stations[summary_prev$metric == "no2_1yr"]

n3a_prev <- summary_prev$n_achieved[summary_prev$metric == "no2_3yr"]
n3_prev  <- summary_prev$n_stations[summary_prev$metric == "no2_3yr"]

same_pct_prev <- isTRUE(all.equal(p1_prev, p3_prev))

no2_standards_sentence_prev <- if (!same_pct_prev) {
  paste0(
    "The annual standard was met at ", n1a_prev, " of the ", n1_prev, " stations (", p1_prev,
    "%) for which valid data were obtained, while the 1-hour standard was met at ",
    n3a_prev, " of the ", n3_prev, " stations (", p3_prev, "%) with sufficient data for analysis."
  )
} else {
  paste0(
    "The annual and 1-hour standards were met at ", p1_prev,
    "% of stations with sufficient data (", n1a_prev, "/", n1_prev,
    " and ", n3a_prev, "/", n3_prev, " stations, respectively)."
  )
}

# Summaries to consult when writing descriptions....

# Which Achieved or Not
# read_rds(here("data/datasets/rep_year_2024/az_ambient.rds")) %>%
#   select(airzone, metric, caaqs_ambient) %>%
#   arrange(metric, caaqs_ambient) %>%
#   pivot_wider(names_from = metric, values_from = caaqs_ambient)

# read_rds(here("data/datasets/rep_year_2024/az_mgmt.rds")) %>%
#   select(airzone, mgmt_level, rep_metric)

```

British Columbia has a network of air quality monitoring stations that measure nitrogen dioxide and other air contaminants. This indicator reports on the concentration of nitrogen dioxide from two reporting periods, `r year_range_previous` and `r year_range`. The data are reported as two metrics: an annual metric based on one year of data, and a 1-hour metric based on three consecutive years of data. These metrics are compared against the [Canadian Ambient Air Quality Standards](https://www.ccme.ca/en/air-quality-report#slide-7) to determine achievement and to define colour-based management levels. CAAQS were established by the [Canadian Council of Ministers of the Environment](http://www.ccme.ca) in 2012 as a key element of the Air Quality Management System that collaboratively and comprehensively manages air quality in Canada.

\begin{center}

\fbox{
  \begin{minipage}[c]{15cm}
    
      \begingroup\centering{\textbf{Nitrogen Dioxide (NO$_{\text{2}}$): Canadian Ambient Air Quality Standard}}
      
      \endgroup
      
      \vspace{1mm}
          
      NO$_{\text{2}}$ levels are calculated using \textbf{two} \hyperref[metric-info]{statistical forms called the annual metric and the 1-hour metric}. The Canadian Ambient Air Quality Standard value for NO$_{\text{2}}$ annual is \textbf{`r no2_lvls[["no2_1yr"]]` parts per billion} and the standard value for NO$_{\text{2}}$ 1-hour is \textbf{`r no2_lvls[["no2_3yr"]]`} parts per billion
          
      \vspace{2mm}
      
      NO$_{\text{2}}$ standards are achieved when annual levels are 
      $\leq$`r no2_lvls[["no2_1yr"]]` ppb and 
      1-hour levels are $\leq$`r no2_lvls[["no2_3yr"]]` ppb. More stringent 2025 CAAQS for NO$_{\text{2}}$ apply in the next reporting period (2023-2025), with an annual metric of 12 ppb and 1-hour metric of 42 ppb.
          
  \end{minipage}
}


\fbox{
  \begin{minipage}[c]{15cm}
  
    \begingroup\centering{\textbf{What is an Air Zone?}}
    
    \endgroup
    
    \vspace{1mm}
    
    \text{British Columbia is divided up into seven air zones, which are areas that typically}
    
    \text{exhibit similar air quality characteristics, issues, and trends.}
    
  \end{minipage}
}
\end{center}
\vspace{2mm}

-   **Nitrogen dioxide (NO~2~) is a gaseous pollutant.** It forms along with other nitrogen oxides (NOx) when fossil fuels are burned in diesel trucks, cars, ships, power plants, and industrial facilities. 
-   **Nitrogen dioxide can harm human health.** Long-term exposure has been linked to allergic responses, asthma, greater susceptibility to respiratory infections (including COVID-19), and effects on the heart and reproductive system. Short-term exposure can reduce lung function and aggravate respiratory symptoms and airway inflammation. These effects have no known safe limits - they can occur even at low concentrations.
- **Nitrogen dioxide and other nitrogen oxides can also harm the environment.** They affect plant growth, contribute to acid rain, and play a role in forming ground-level ozone --- all of which can damage ecosystems. NO~2~ is also responsible for the reddish-brown haze sometimes seen over cities.
-   **2021-2023: nitrogen dioxide levels met the Canadian Ambient Air
    Quality Standards at `r min(summary_prev$pct_achieved)`
    percent of assessed monitoring stations in B.C.** There are two metrics 
    for NO~2~---an annual standard and a
    1-hour standard (see sidebar). `r no2_standards_sentence_prev`
-   **2022-2024: nitrogen dioxide levels met the Canadian Ambient Air
    Quality Standards at `r min(print_summary$percent_achieved)`
    percent of assessed monitoring stations in B.C.** `r no2_standards_sentence`
-   **During both periods, nitrogen dioxide levels met both of the Canadian Ambient
    Air Quality Standards in `r as.character(english(summary_prev$az_achieved[summary_prev$metric=="no2_1yr"]))` of B.C.'s seven air zones.** 
    Currently, there are no 
    [air monitoring stations](http://www2.gov.bc.ca/gov/content?id=292EC5BD62A149A192B7DD2CE155E33E)
    in the Northwest air zone.
    <!-- See the summaries calculated in the starting RMD chunk for information 
     needed to fill in the above bullet point. -->
-   **Nitrogen dioxide levels are used to set management levels
    for each air zone.** The four management levels and the recommended actions are: (1) green (actions for keeping clean areas clean); (2) yellow (actions for preventing air quality deterioration); (3) orange (actions for preventing Canadian Ambient Air Quality Standard exceedance); and (4) red (actions for achieving air zone Canadian Ambient Air Quality Standard). Each management level corresponds to actions that become more rigorous as the level of NO~2~ approaches CAAQS. Suggested actions for each management level are outlined in the [Guidance Document on Air Zone Management](https://ccme.ca/en/res/guidancedocumentonairzonemanagement_secured.pdf#page=15).
    
The maps and charts below summarise the Canadian Ambient Air Quality Standard 
achievement status for nitrogen dioxide in B.C. air zones, as
well as both the annual and 1-hour NO~2~ levels at individual
monitoring stations. Summaries are given for each monitoring station where
sufficient data were available for the `r year_range` and `r year_range_previous` reporting periods.

# Status of 1-hour NO~2~ Levels in B.C. Air Zones (`r year_range`)

```{r achievement_map_3yr, fig.height=8}
plots[["achievement_map_3yr"]]
```


\newpage

# Status of Annual NO~2~ Levels in B.C. Air Zones (`r year_range`)

```{r achievement_map_1yr, fig.height=8}
plots[["achievement_map_1yr"]]
```

\newpage

# NO~2~ Metrics for Air Monitoring Stations within B.C. Air Zones (`r year_range`)

```{r no2_ambient_summary_plot, fig.height=9}
plots[["no2_ambient_summary_plot"]]
```

# Status of 1-hour NO~2~ Levels in B.C. Air Zones (`r year_range_previous`)

```{r achievement_map_3yr_2023, fig.height=8}
plots[["achievement_map_3yr"]]
```


\newpage

# Status of Annual NO~2~ Levels in B.C. Air Zones (`r year_range_previous`)

```{r achievement_map_1yr_2023, fig.height=8}
plots_2023[["achievement_map_1yr"]]
```

\newpage

# NO~2~ Metrics for Air Monitoring Stations within B.C. Air Zones (`r year_range_previous`)

```{r no2_ambient_summary_plot_2023, fig.height=9}
plots_2023[["no2_ambient_summary_plot"]]
```

\hyperdef{}{metric-info}{}
### More about the Canadian Ambient Air Quality Standard nitrogen dioxide metrics:

-   There are two Canadian Ambient Air Quality Standards for nitrogen dioxide 
    (NO~2~). The statistical form of the NO~2~ annual
    metric is the average over a single calendar year of all 1-hour average
    concentrations of NO~2~. The statistical form of the NO~2~ 1-hour metric is 
    the 3-year average of the annual 98th percentile (typically 8th highest) of the daily maximum 1-hr 
    average concentrations of NO~2~.
-   The NO~2~ metric for an air zone is the highest NO~2~ metric value
    reported from monitoring stations within the air zone. 
-   Criteria for data completeness and sufficiency of the two NO~2~ metrics are described in the [Guidance Document on Achievement Determination: Canadian Ambient Air Quality Standards for Nitrogen Dioxide (2020)](https://ccme.ca/en/res/gdadforcaaqsfornitrogendioxide_en1.0.pdf).
-   Air quality monitoring stations with at least two years of valid data from the `r year_range` and `r year_range_previous` reporting periods were included in this indicator. Visit [Current Air Quality  Data](http://www2.gov.bc.ca/gov/content?id=292EC5BD62A149A192B7DD2CE155E33E) for a complete list of currently active air quality monitoring stations across B.C.

### Canada-wide Air Quality Management System

The Air Quality Management System is Canada's approach for protecting
air quality. Under the Air Quality Management System, provinces and
territories monitor, report and manage local air quality within air
zones, with the goal of continuously improving air quality and keeping
pollutants below the Canadian Ambient Air Quality Standards.

-   There are seven air zones in British Columbia: Coastal, Georgia
    Strait, Lower Fraser Valley, Southern Interior, Central Interior,
    Northeast and Northwest.
-   The Air Zone Management Framework defines air zone management levels
    for nitrogen dioxide based on the higher of the annual and
    1-hour nitrogen dioxide levels reported from monitoring
    stations within the air zone.
-   The four management levels are (1) green (actions for keeping clean
    areas clean); (2) yellow (actions for preventing air quality
    deterioration); (3) orange (actions for preventing Canadian Ambient
    Air Quality Standard exceedance); and (4) red (actions for achieving
    air zone Canadian Ambient Air Quality Standard). Each management
    level is associated with a suite of actions that become more
    rigorous as nitrogen dioxide levels approach the standard.
    Actions for each management level are detailed in the [Guidance Document on Air Zone Management (2019)
    (PDF)](https://ccme.ca/en/res/guidancedocumentonairzonemanagement_secured.pdf).
-   The Lower Fraser Valley air zone was assigned to a red management level; 
    the Central Interior, Georgia Strait, Northeast, and Southern Interior air
    zones were assigned to an orange management level; and the Coastal air zone
    was assigned to a yellow management level. 
    There are currently no 
    [air monitoring stations](http://www2.gov.bc.ca/gov/content?id=292EC5BD62A149A192B7DD2CE155E33E)
    in the Northwest air zone.
    
<!-- See the summaries calculated in the starting RMD chunk for information 
     needed to fill in the above bullet point. -->

\newpage
    
# Air Quality Management Levels in B.C. Air Zones (`r year_range`)  

```{r no2_mgmt_map, fig.height=9}
plots[["no2_mgmt_map"]]
```

\newpage

# Station-Level Air Quality Management Levels Within Air Zones (`r year_range`)

```{r no2_mgmt_chart, fig.height=8}
plots[["no2_mgmt_chart"]]
```

# Air Quality Management Levels in B.C. Air Zones (`r year_range_previous`)  

```{r no2_mgmt_map_2023, fig.height=9}
plots_2023[["no2_mgmt_map"]]
```

\newpage

# Station-Level Air Quality Management Levels Within Air Zones (`r year_range_previous`)

```{r no2_mgmt_chart_2023, fig.height=8}
plots_2023[["no2_mgmt_chart"]]
```

#### More about the Air Quality Management System management levels:

-   There can be cases when an air zone does not achieve a given
    Canadian Ambient Air Quality Standard because of sources over which
    jurisdictions have little or no control, such as those related to
    transboundary flows and exceptional events, like forest fires.
-   Prior to determining management levels, jurisdictions have the
    option of adjusting their air zone metric values to remove such
    external influences. These arrangements aim to ensure that
    jurisdictions are responsible for managing only the emissions
    sources they can control.
-   Wildfires are generally the largest contributor to transboundary
    flows and exceptional events in B.C. Over the `r year_range` reporting
    period, `r #tfee$n_sites` stations had one or more days during the wildfire season
    (May-October) where the daily nitrogen dioxide
    concentration was determined to be influenced by smoke from
    wildfires and exceeded the 1-hour standard of 
    `r no2_lvls[["no2_3yr"]]` ppb. The
    majority of wildfire influences occurred in 2018 and 2020. Those daily
    concentrations were removed from the calculations of management
    levels, resulting in a change from red to orange for the Central Interior
    and Georgia Strait air zones; from red to yellow for the Northeast air zone.

<!-- See the summaries calculated in the starting RMD chunk for information 
     needed to fill in the above bullet point. -->

### Methods

The methods used to develop this indicator---including procedures, data
requirements, and calculation of the Canadian Ambient Air Quality
Standard nitrogen dioxide metrics---are detailed in the [Guidance Document on Achievement Determination: Canadian Ambient Air Quality Standards for Nitrogen Dioxide (2020)](https://ccme.ca/en/res/gdadforcaaqsfornitrogendioxide_en1.0.pdf)
published by the [Canadian Council of Ministers of the
Environment](http://www.ccme.ca).

**R package and code:** We have developed an
[**R**](http://www.r-project.org) package to facilitate the calculation
of air quality metrics according to the [Canadian Ambient Air Quality
Standards](https://www.ccme.ca/en/air-quality-report#slide-7).
Download the 'rcaaqs' package from
[GitHub](https://github.com/bcgov/rcaaqs). The source code for repeating
the analysis presented on this page is also available on
[GitHub](https://github.com/bcgov/no2-caaqs-analysis).

### References and Other Useful Links

-   [Access B.C.'s real-time data on air pollutants and find locations of all provincial air monitoring stations in B.C.](http://www2.gov.bc.ca/gov/content?id=292EC5BD62A149A192B7DD2CE155E33E)
-   [BC Lung Association's BC State of the Air Reports](https://bclung.ca/lung-health/air-quality/state-of-the-air-report-archives/)
-   [Canadian Ambient Air Quality Standards](https://www.ccme.ca/en/air-quality-report#slide-7)
-   [Canadian Council of Ministers of the Environment](https://www.ccme.ca/en)
-   [Canadian Environmental Sustainability Indicators: Air Indicators](https://www.canada.ca/en/environment-climate-change/services/environmental-indicators/air.html)
-   [Canadian Smog Science Assessment: Highlights and Key Messages](http://publications.gc.ca/site/eng/9.694820/publication.html)
-   [Guidance Document on Achievement Determination for Canadian Ambient Air Quality Standards for Nitrogen Dioxide](https://ccme.ca/en/res/gdadforcaaqsfornitrogendioxide_en1.0.pdf)
-   [Guidance Document on Air Zone Management](https://ccme.ca/en/res/guidancedocumentonairzonemanagement_secured.pdf)
-   [Learn more about the implementation of the Air Quality Management System in British Columbia](http://www2.gov.bc.ca/gov/content?id=8FA84ADC845A49AB93E525A58D9D4A97)
-   Read individual [Air Zone reports](https://www2.gov.bc.ca/gov/content/environment/air-land-water/air/reports/latest-air-zone-reports) on the achievement of the Canadian Ambient Air Quality Standards in B.C.


### Data

\*By accessing these datasets, you agree to the licence associated with
each file, as indicated in parentheses below.

-   [Indicator data: BC Nitrogen Dioxide Canadian Ambient Air
    Quality Standards
    `r year_range`](https://catalogue.data.gov.bc.ca/dataset/indicator-summary-data-bc-nitrogen-dioxide-canadian-ambient-air-quality-standards) (`r get_data_license("ogl-bc")`)
-   [BC NO~2~ Hourly Data & Air Monitoring Station
    locations](https://catalogue.data.gov.bc.ca/dataset/77eeadf4-0c19-48bf-a47a-fa9eef01f409) (`r get_data_license("ogl-bc")`)
-   [BC Air
    Zones](https://catalogue.data.gov.bc.ca/dataset/e8eeefc4-2826-47bc-8430-85703d328516) (`r get_data_license("ogl-bc")`)

Published and Available On-Line at Environmental Reporting BC:
<http://www.env.gov.bc.ca/soe/indicators/air/fine_pm.html>

Email correspondence to: envreportbc@gov.bc.ca

*Suggested Citation*:  
Environmental Reporting BC. `r format(Sys.Date(), "%Y")`. Status of Nitrogen Dioxide in B.C. (`r paste0(year_range_previous, " & ", year_range)`). State of Environment Reporting, Ministry of Environment and Parks, British Columbia, Canada.

# Appendix: Detailed nitrogen dioxide Canadian Ambient Air Quality Standard results for each monitoring station within air zones in B.C.

\vspace{1cm}


```{r appendix, results='asis', fig.width = 9, fig.asp = 0.4}

iwalk(stn_plots,  ~ {
  
  stn <- filter(no2_results, site == .y) %>%
    complete(airzone, site, metric = c("no2_1yr", "no2_3yr"), 
             fill = list(caaqs_ambient = "Insufficient Data"))
  stn_3yr <- filter(stn, metric == "no2_3yr")
  stn_1yr <- filter(stn, metric == "no2_1yr")
  
  # Airzone & Site block
  cat("\\hrule")
  cat("\\textbf{Air Zone:} ", stn$airzone[1], "\\newline")
  cat("\\textbf{Monitoring Station:} ", knitr_latex_char(stn$site[1]), "\\newline")
  cat("\\vspace{-0.2cm} \n \n \\hrule \n \n \\vspace{0.5cm}")
  
  # 24h - CAAQS
  cat("\\textbf{NO$_{2}$ 1-hour Air Quality Standard:} ",
      as.character(stn_3yr$caaqs_ambient), "\\newline")
  
  # 24h - Value
  if(is.na(stn_3yr$metric_value_ambient)) {
    cat("\\textbf{NO$_{2}$ 1-hour Metric:} Unknown \\newline \\newline ", sep = "")
  } else {
    cat("\\textbf{NO$_{2}$ 1-hour Metric:} ",
        stn_3yr$metric_value_ambient, "ppb (", 
        stn_3yr$n_years, " year average) \\newline ", "\\newline ", sep = "")
  }
    
  # 24h - Plot
  if(!is.null(.x[["3yr"]])) plot(.x[["3yr"]])
  cat("\n \n \\vspace{0.75cm} \n ") # Need line breaks or \vspace applies to next line
  
  
  # annual - CAAQS
  cat("\\textbf{NO$_{2}$ Annual Air Quality Standard:} ",
      as.character(stn_1yr$caaqs_ambient), " \\newline ")
  
  # annual - Value
  if(is.na(stn_1yr$metric_value_ambient)) {
    cat("\\textbf{NO$_{2}$ Annual Metric:} Unknown \\newline \\newline ", sep = "")
  } else {
    cat("\\textbf{NO$_{2}$ Annual Metric:} ",
        stn_1yr$metric_value_ambient, "ppb (", 
        stn_1yr$n_years, " year average) \\newline ", "\\newline ", sep = "")
  }
  
  # annual - Plot
  if(!is.null(.x[["1yr"]])) plot(.x[["1yr"]])
  
  cat("\\newpage")
})

```
